My title

### 2024-10-22 paper/paper.qmd
Update the paper.

library(tidyverse)
```

@@

analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))

@@

@@

# Pollster Methodology Overview and Evaluation

## Overview of SurveyUSA\
SurveyUSA is a privately held opinion research company that operates nationwide, across all 50 U.S. states. Since its founding, the company has conducted over 40,000 research projects, serving a client base of 400 organizations, including media outlets, corporations, non-profits, government agencies, and academic institutions. Known for its expertise in localized opinion research, SurveyUSA focuses on gathering data at the city, county, and regional levels. The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms.

## Population, Frame, and Sample\

* Target Population: U.S. citizens eligible to vote in the 2024 presidential election.\
* Sample Frame:  U.S. households with either home telephones or access to devices such as phones or tablets. \
* Sample Size: Sample sizes vary across different polls. For the 2024 U.S. presidential election cycle, SurveyUSA conducted 49 polls, with sample sizes ranging from 507 to 2,330 for registered voters or likely voters. The average sample size for these polls is approximately 1,045 households.\

## Recruitment\
SurveyUSA employs a mixed-method approach to recruitment, including online panels, telephone calls, and a text-to-web method. Some respondents are recruited through Random Digit Dialing (RDD) using telephone samples purchased from Aristotle, while others, who do not use home telephones, are invited to complete the survey on an electronic device such as a phone or tablet. Respondents from non-probability online panels are selected randomly by Cint/Lucid Holdings LLC.\

## Sampling approach and Trade-offs\
SurveyUSA uses a blend of probability and non-probability sampling methods. Some respondents are drawn from non-probability online panels, while others are recruited using probability-based telephone sampling. Responses are weighted based on the latest U.S. Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population. Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects.\

* **Advantages:**\
The diverse sampling approach not only ensures a broad range of opinions is captured but also complements probability-based sampling, which accurately reflects the overall population. Furthermore, reweighting the data according to U.S. Census demographics strengthens the credibility of the results by ensuring demographic accuracy. Additionally, rotating questions and answer choices helps mitigate bias, further improving the reliability of the data. Finally, the use of online surveys offers a cost-effective solution for efficient data collection.\
* **Disadvantages:**\
Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews. Additionally, challenges like non-response issues, such as busy signals or refusals to participate, can hinder the effectiveness of the data collection process.\

## Non-response Handling\
In cases of non-response, SurveyUSA attempts follow-up calls if interviews are interrupted by answering machines or busy signals. Weighting is applied to adjust for non-response bias, although this doesn't completely eliminate challenges posed by unreachable or unwilling participants.\

## Questionnaire Evaluation\

* **Positive Aspects:**
A logical flow between questions facilitates easy navigation for respondents throughout the survey, while simple wording promotes inclusivity by enabling individuals from diverse backgrounds to comprehend the questions. Furthermore, all questions are directly relevant to analyzing the 2024 U.S. presidential election, and providing predefined response options simplifies the choices for participants.\
* **Negative Aspects:**
Static options for party affiliation and ideology may fail to capture the nuances of respondents’ political beliefs. These rigid categories could oversimplify complex political identities.\

## Summary Evaluation\
SurveyUSA’s methodology reflects a balanced approach, leveraging various sampling approach and method to reach a representative sample. While its blend of probability and non-probability methods has strengths, such as cost-effectiveness and broad reach, it faces challenges related to telephone interview logistics, potential interviewer bias, and the limitations of fixed questionnaire options. Nevertheless, the inclusion of data weighting and question rotation adds credibility to its results, making SurveyUSA a reliable pollster for localized opinion research.

@@

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

@@

>>>>

library(tidyverse)
analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
```

@@

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

```{r}
trump_model <- readRDS(here::here(("models/trump_model.rds")))
```

# Diagnostic plots for the MLR model
par(mfrow = c(2, 2))
plot(mlr_harris_model)
par(mfrow = c(1, 1))  # Reset plot layout

@@

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(trump_model, "trace")

plot(first_model, "rhat")

@@

# Acknowledgements
@citeR
